Forecasting 2024 US election using linear regression

### 2024-10-28 paper/paper.qmd
update with merged version

This work is licensed under a [Creative Commons Attribution 4.0
International License](https://creativecommons.org/licenses/by/4.0/).
You are free to share, copy, redistribute, remix, transform, and build
upon the material for any purpose, even commercially, as long as you
credit the original creation.

>>>>

This work is licensed under a [Creative Commons Attribution 4.0
International License](https://creativecommons.org/licenses/by/4.0/).
We are free to share, copy, redistribute, remix, transform, and build
upon the material for any purpose, even commercially, as long as we
credit the original creation.
